Throughput Prediction on 60 GHz Devices for Latency Sensitive Applications

### 2021-01-21 paper.tex
changes

For all our experiments, we keep the phone in a Google
Cardboard~\cite{cardboard} headset at a distance of 4 m from the
AP. We used nuttcp~\cite{nuttcp} to generate TCP traffic and log
throughput every 10 ms. We developed an Android application which runs
on the phone and uses the Android Sensor API~\cite{android-sensor} to
log information from the
$\tt{TYPE\_ROTATION\_VECTOR}$/$\tt{TYPE\_GAME\_ROTATION\_VECTOR}$. These
sensors report the angle (in radians, which we convert to degrees) the
phone has moved in the azimuth, pitch, or roll directions. We also log
data from the accelerometer ($\tt{TYPE\_ACCELEROMETER}$) sensor, which
gives the acceleration of the phone (in m/s$^2$) in the x-, y-, and
z-axis. Data from both the sensors are logged every 10 ms.

>>>>

For all our experiments, we keep the phone in a Google
Cardboard~\cite{cardboard} headset at a distance of 4 m from the
AP. We used nuttcp~\cite{nuttcp} to generate TCP traffic and log
throughput every 10 ms. We developed an Android application that runs
on the phone and uses the Android Sensor API~\cite{android-sensor} to
log information from the
$\tt{TYPE\_ROTATION\_VECTOR}$/$\tt{TYPE\_GAME\_ROTATION\_VECTOR}$. These
sensors report the angle (in radians, which we convert to degrees) that the
phone has moved in the azimuth, pitch, or roll directions. We also log
data from the accelerometer ($\tt{TYPE\_ACCELEROMETER}$) sensor, which
gives the acceleration of the phone (in m/s$^2$) in the x-, y-, and
z-axis. Data from both the sensors are logged every 10 ms.
